---
title: "Children Hypertension Check"
author: "Rustem"
output: ioslides_presentation
---

## Hypertension

Hypertension (HTN) or high blood pressure is a chronic medical condition in which the blood pressure in the arteries is elevated.

Hypertension puts strain on the heart, leading to hypertensive heart disease and coronary artery disease. Hypertension is also a major risk factor for stroke, aneurysms of the arteries, peripheral arterial disease and chronic kidney disease.

## Diagnosis
Hypertension is diagnosed, if the **daily average of the systolic blood pressure** is higher than the *maximum normal value*, which differs for boys and girls and depends on the height.

The maximum normal values for different conditions are available in
the `htn.csv` data set at the [repository][2].

```{r }
htn <- read.csv('htn.csv')
```

## Maximum Normal Value
The following scatterplot can be used for determining the maximum normal value
for a certain height for boys and girls.

```{r echo=FALSE}
library(ggplot2)

gp <-ggplot(htn, aes(x=Height, y=Systolic, color=Gender))
gp <- gp + geom_point(size=4)
gp <- gp + scale_x_continuous(name='Height, cm')
gp <- gp + scale_y_continuous(name='Systolic blood pressure, mmHg')
print(gp)
```

## Children Hypertension Check App
You can also use the [Children Hypertension Check ShinyApp][1] to determine,
if a certain child has hypertension.


[1]:    https://rfstest.shinyapps.io/hypertension/
[2]:    https://github.com/rfstest/hypertension

